---
title: "Final Project Dashboard : Models of Neigbourhood Change in San Diego, California"
output:
  html_document:
    theme: readable
    highlight: tango
    toc: true
    self_contained: false
    number_sections: false
    css: textbook.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=T, fig.width=10, fig.height=6, warning=F, message=F )
```


```{r}
library( geojsonio )   # read shapefiles
library( sp )          # work with shapefiles
library( sf )          # work with shapefiles - simple features format
library( mclust )      # cluster analysis 
library( tmap )        # theme maps
library( ggplot2 )     # graphing 
library( ggthemes )    # nice formats for ggplots
library( dplyr )       # data wrangling 
library( pander )      # formatting RMD tables
library( stargazer )
library( scales )
library( tidycensus )
library( cartogram )  # spatial maps w/ tract size bias reduction
#library( maptools )   # spatial object manipulation 
library( corrplot )   # correlation plots 
```


```{r}
crosswalk <- read.csv( "https://raw.githubusercontent.com/DS4PS/cpp-529-master/master/data/cbsatocountycrosswalk.csv",  stringsAsFactors=F, colClasses="character" )

grep ( "^SAN DIEGO", crosswalk$msaname, value=TRUE ) 
```


```{r}
these.sd <- 
  crosswalk$msaname == grep ( "^SAN DIEGO", crosswalk$msaname, value=TRUE ) 

these.fips <- crosswalk$fipscounty[ these.sd ]
these.fips <- na.omit( these.fips )
```


```{r, install=TRUE}
# set the api key
census_api_key( "1f6f30cb3efe7bd63a29c29429a5880a38e002d7" )

# Filter for San Diego County
these.fips <- "06073"

state.fips <- substr( these.fips, 1, 2 )
county.fips <- substr( these.fips, 3, 5 )

cbind( these.fips, state.fips, county.fips ) %>% pander()
```

```{r, tigris_use_cache = TRUE}
#May need to install and load in pak
#pak::pak("walkerke/tigris@ftp-patch")


sd.pop <- get_acs( geography = "tract", variables = "B01003_001",
         state = "06", county = "073", geometry = TRUE ) %>% 
         select( GEOID, estimate ) %>%
         rename( POP=estimate )
# Recode GEOID to match Census formatting (remove leading zero)

sd.pop$GEOID <- substr(sd.pop$GEOID, 2, nchar(sd.pop$GEOID))

# Save the dataframe 'sd.pop' to an RData file:
#save(sd.pop, file = "sd.pop.RData")
```

**Step 3: Add Census Data **

Here, we use specific data stored in the github URl with multiple variables associated.

```{r}
URL <- "https://github.com/DS4PS/cpp-529-master/raw/master/data/ltdb_std_2010_sample.rds"
census.dat <- readRDS(gzcon(url( URL )))
```

**Step 4: Transforming Shapefile into a Dorling Cartogram**

```{r}
# Merge the downloaded population data with the additional data
sd <- merge(sd.pop, census.dat, by.x="GEOID", by.y="tractid")

# make sure there are no empty polygons
sd <- sd[ ! st_is_empty( sd ) , ]

# Convert the simple features object (sf) to SpatialPolygonsDataFrame (sp)
sd.sp <- as_Spatial(sd)

# Check the class of the object to confirm conversion
class(sd.sp)
# Plot spatial data to visually inspect it
plot(sd.sp)
```


```{r}
# Transform map projection to Mercator (EPSG:3395) and remove empty or zero population tracts
sd.sp <- spTransform(sd.sp, CRS("+init=epsg:3395"))
sd.sp <- sd.sp[sd.sp$POP != 0 & (!is.na(sd.sp$POP)), ]

# Create Dorling cartogram (circles sized by population)
# Weight (pop.w) is normalized by the maximum population
sd.sp$pop.w <- sd.sp$POP / 38907  # normalization factor
sd_dorling <- cartogram_dorling(x = sd.sp, weight = "pop.w", k = 0.05)

# Save Dorling cartogram to GeoJSON file (optional)
# geojson_write(sd_dorling, file = "San_Diego.geojson", geometry = "polygon")
plot( sd_dorling )
```



```{r}
sd_dorling_sf <- st_as_sf(sd_dorling)

tm_shape( sd_dorling_sf ) + 
  tm_polygons( 
    size="POP", col="hinc12", n=7, style="quantile", palette="brewer.spectral" ) + 
   tm_layout( "Dorling Cartogram \nof Household Income \nfor San Diego", 
              title.position=c( "right","top" ) )
```


```{r}
names(sd)
```


**Step 5 : Prepare Data for Clustering**

```{r}
these.sd <- c("pnhwht12", "pnhblk12", "phisp12", "pntv12", "pfb12", "polang12",  
"phs12", "pcol12", "punemp12", "pflabf12", "pprof12", "pmanuf12", 
"pvet12", "psemp12", "hinc12", "incpc12", "ppov12", "pown12", 
"pvac12", "pmulti12", "mrent12", "mhmval12", "p30old12", "p10yrs12", 
"p18und12", "p60up12", "p75up12", "pmar12", "pwds12", "pfhh12")

d1 <- sd_dorling@data
d2 <- select( d1, these.sd )
d3 <- apply( d2, 2, scale )

```

**Step 6: Apply K-means Clustering**

```{r}
set.seed( 1234 )
fit <- Mclust( d3 )
sd_dorling_sf$cluster <- as.factor( fit$classification )
summary( fit )
```

```{r}
plot( fit, what = "classification" )
```

**Step 7: Visualize and Interpret the Clusters**

```{r}
data.dictionary <- 
structure( 
  list( 
    LABEL = c( "pnhwht12", "pnhblk12", "phisp12", 
               "pntv12", "pfb12", "polang12", "phs12", "pcol12", "punemp12", 
               "pflabf12", "pprof12", "pmanuf12", "pvet12", "psemp12", "hinc12", 
               "incpc12", "ppov12", "pown12", "pvac12", "pmulti12", "mrent12", 
               "mhmval12", "p30old12", "p10yrs12", "p18und12", 
               "p60up12", "p75up12", "pmar12", "pwds12", "pfhh12" ), 
    VARIABLE = c( "Percent white, non-Hispanic", 
                 "Percent black, non-Hispanic", "Percent Hispanic", 
                 "Percent Native American race", "Percent foreign born", 
                 "Percent speaking other language at home, age 5 plus", 
                 "Percent with high school degree or less", 
                 "Percent with 4-year college degree or more", 
                 "Percent unemployed", "Percent female labor force participation", 
                 "Percent professional employees", 
                 "Percent manufacturing employees", 
                 "Percent veteran", "Percent self-employed", 
                 "Median HH income, total", "Per capita income", 
                 "Percent in poverty, total", "Percent owner-occupied units", 
                 "Percent vacant units", "Percent multi-family units", 
                 "Median rent", "Median home value", 
                 "Percent structures more than 30 years old",
                 "Percent HH in neighborhood 10 years or less", 
                 "Percent 17 and under, total", "Percent 60 and older, total",
                 "Percent 75 and older, total", 
                 "Percent currently married, not separated", 
                 "Percent widowed, divorced and separated", 
                 "Percent female-headed families with children" ) ), 
  class = "data.frame", row.names = c( NA, -30L ) )
data.dictionary %>% pander()
```


```{r}
df.pct <- sapply( d2, ntile, 100 )
d4 <- as.data.frame( df.pct )
d4$cluster <- as.factor( paste0("GROUP-",fit$classification) )

num.groups <- length( unique( fit$classification ) )

stats <- 
d4 %>% 
  group_by( cluster ) %>% 
  summarise_each( funs( mean ) )

t <- data.frame( t( stats ), stringsAsFactors=FALSE )
names( t ) <- paste0( "GROUP.", 1:num.groups )
t <- t[-1,]


for( i in 1:num.groups )
{
  z <- t[,i]
  plot( rep(1,30), 1:30, bty="n", xlim=c(-75,100), 
        type="n", xaxt="n", yaxt="n",
        xlab="Percentile", ylab="",
        main=paste( "GROUP",i ) )
  abline( v=seq( 0, 100, 25 ), lty=3, lwd=1.5, col="gray90" )
  segments( y0=1:30, x0=0, x1=100, col="gray70", lwd=2 )
  text( -0.2, 1:30, data.dictionary$VARIABLE, cex=0.85, pos=2 )
  points( z, 1:30, pch=19, col="firebrick", cex=1.5 )
  axis( side=1, at=c( 0,50,100 ), col.axis="gray", col="gray" )
}
```

The labels for the groups are:

Group 1-White, native American/Veteran/Self employed;

Group 2-Multi-family/Educated/Active females;

Group 3-Non-white,unemployed minorities;

Group 4-Older affluent white/Stable Families;

Group 5-Foreign-born/Multilingual/Single Mothers;

Group 6-Mixed-race, high income employees/high home value.

```{r}
# libraries
library( dplyr )
library( knitr )
library( pander )
library( stargazer )
library( scales )


# set seed for reproducible results
set.seed( 1234 )


# stargazer settings
s.type <- "text"  
#s.type <- "html"


# helper function
panel.cor <- function(x, y, digits=2, prefix="", cex.cor)
{
    usr <- par("usr"); on.exit(par(usr))
    par(usr = c(0, 1, 0, 1))
    r <- abs(cor(x, y))
    txt <- format(c(r, 0.123456789), digits=digits)[1]
    txt <- paste(prefix, txt, sep="")
    if(missing(cex.cor)) cex <- 0.8/strwidth(txt)
    
    test <- cor.test(x,y)
    # borrowed from printCoefmat
    Signif <- symnum(test$p.value, corr = FALSE, na = FALSE,
                  cutpoints = c(0, 0.001, 0.01, 0.05, 0.1, 1),
                  symbols = c("***", "**", "*", ".", " "))
    
    text(0.5, 0.5, txt, cex = 1.5 )
    text(.7, .8, Signif, cex=cex, col=2)
}

panel.smooth <- function (x, y, col = par("col"), bg = NA, pch = par("pch"), 
    cex = 0.5, col.smooth = "red", span = 2/3, iter = 3, ...) 
{
    points(x, y, pch = 19, col = gray(0.7,0.2), bg = bg, cex = cex)
    ok <- is.finite(x) & is.finite(y)
    if (any(ok)) 
        lines(stats::lowess(x[ok], y[ok], f = span, iter = iter), 
            col = col.smooth, lwd=2, ...)
}

# custom plot
jplot <- function( x1, x2, lab1="", lab2="", draw.line=T, ... )
{

    plot( x1, x2,
          pch=19, 
          col=gray(0.6, alpha = 0.2), 
          cex=0.5,  
          bty = "n",
          xlab=lab1, 
          ylab=lab2, cex.lab=1.5,
        ... )

    if( draw.line==T ){ 
        ok <- is.finite(x1) & is.finite(x2)
        lines( lowess(x2[ok]~x1[ok]), col="red", lwd=3 ) }

}
```


```{r}
URL1 <- "https://github.com/DS4PS/cpp-529-fall-2020/raw/main/LABS/data/rodeo/LTDB-2000.rds"
d1 <- readRDS( gzcon( url( URL1 ) ) )

URL2 <- "https://github.com/DS4PS/cpp-529-fall-2020/raw/main/LABS/data/rodeo/LTDB-2010.rds"
d2 <- readRDS( gzcon( url( URL2 ) ) )

URLmd <- "https://github.com/DS4PS/cpp-529-fall-2020/raw/main/LABS/data/rodeo/LTDB-META-DATA.rds"
md <- readRDS( gzcon( url( URLmd ) ) )

d1 <- select( d1, - year )
d2 <- select( d2, - year )

d <- merge( d1, d2, by="tractid" )
d <- merge( d, md, by="tractid" )
```



```{r, eval=FALSE}
table( d$urban )
```

```{r}
d <- filter( d, urban == "urban" )
```

```{r}
d <- select( d, tractid, 
             mhmval00, mhmval12, 
             hinc00, 
             hu00, vac00, own00, rent00, h30old00,
             empclf00, clf00, unemp00, prof00,  
             dpov00, npov00,
             ag25up00, hs00, col00, 
             pop00.x, nhwht00, nhblk00, hisp00, asian00,
             cbsa, cbsaname )
d <- d %>%
  mutate( # percent white in 2000
          p.white = 100 * nhwht00 / pop00.x,
          # percent black in 2000
          p.black = 100 * nhblk00 / pop00.x,
          # percent hispanic in 2000
          p.hisp = 100 * hisp00 / pop00.x, 
          # percent owner-occupied units
          p.own = 100 * own00 / hu00,
          # percent asian in 2000
          p.asian = 100 * asian00 / pop00.x,
          # percent high school grads by age 25 in 2000 
          p.hs = 100 * (hs00+col00) / ag25up00,
          # percent pop with college degree in 2000
          p.col = 100 * col00 / ag25up00,
          # percent employed in professional fields in 2000
          p.prof = 100 * prof00 / empclf00,
          # percent unemployment  in 2000
          p.unemp = 100 * unemp00 / clf00,
          # percent of housing lots in tract that are vacant in 2000
          p.vacant = 100 * vac00 / hu00,
          # dollar change in median home value 2000 to 2010 
          pov.rate = 100 * npov00 / dpov00 )

```

**Create growth of median home value from 2000 to 2010**

```{r}
# Adjust 2000 home values for inflation 
mhv.00 <- d$mhmval00 * 1.28855  
mhv.10 <- d$mhmval12

# Change in MHV in dollars
mhv.change <- mhv.10 - mhv.00
```


**Omit cases that have a median home value less than $1,000 in 2000**
```{r}

# adjust 2000 home values for inflation 
mhv.00 <- d$mhmval00 * 1.28855  
mhv.10 <- d$mhmval12

# change in MHV in dollars
mhv.change <- mhv.10 - mhv.00


# drop low 2000 median home values
# to avoid unrealistic growth rates.
#
# tracts with homes that cost less than
# $1,000 are outliers
mhv.00[ mhv.00 < 1000 ] <- NA

# change in MHV in percent
mhv.growth <- 100 * ( mhv.change / mhv.00 )

d$mhv.00 <- mhv.00
d$mhv.10 <- mhv.10
d$mhv.change <- mhv.change
d$mhv.growth <- mhv.growth

# Average growth in median home value for the city
d <- 
  d %>%
  group_by( cbsaname ) %>%
  mutate( metro.mhv.change = median( mhv.change, na.rm=T ),
             metro.mhv.growth = 100 * median( mhv.growth, na.rm=T ) ) %>%
  ungroup() 
```


**Print summary statistics**
```{r}
# Histograms
# 2000
hist( mhv.00, breaks=200, xlim=c(0,500000), 
      col="gray20", border="white",
      axes=F, 
      xlab="MHV",
      ylab="",
      main="Median Home Value in 2000 (2010 US dollars)" )

axis( side=1, at=seq(0,500000,100000), 
      labels=c("$0","$100k","$200k","$300k","$400k","$500k") )

abline( v=median( mhv.00, na.rm=T ), col="orange", lwd=3 )
```

```{r}
# 2010
hist( mhv.10, breaks=200, xlim=c( 0, max( mhv.10, na.rm = TRUE ) ), 
      col="gray20", border="white",
      axes=F, 
      xlab="MHV",
      ylab="",
      main="Median Home Value in 2010" )

axis( side=1, at=seq(0,1000000,250000), 
      labels=c("$0","$250k","$500k","$750k","$1mil") )

abline( v=median( mhv.10, na.rm=T ), col="lightblue", lwd=3 )
```

**Descriptives**
```{r}
df <- data.frame( MedianHomeValue2000=mhv.00, 
                  MedianHomeValue2010=mhv.10, 
                  MHV.Change.00.to.10=mhv.change,
                  MHV.Growth.00.to.12=mhv.growth )

stargazer( df, 
           type=s.type, 
           digits=0, 
           summary.stat = c("min", "p25","median","mean","p75","max") )
```

**Change in MHV 2000-2010**
```{r}
hist( mhv.change/1000, breaks=500, 
      xlim=c(-100,500), yaxt="n", xaxt="n",
      xlab="Thousand of US Dollars (adjusted to 2010)", cex.lab=1.5,
      ylab="", main="Change in Median Home Value 2000 to 2010",
      col="gray20", border="white" )

axis( side=1, at=seq( from=-100, to=500, by=100 ), 
      labels=paste0( "$", seq( from=-100, to=500, by=100 ), "k" ) )
        
mean.x <- mean( mhv.change/1000, na.rm=T )
abline( v=mean.x, col="darkorange", lwd=2, lty=2 )
text( x=200, y=1500, 
      labels=paste0( "Mean = ", dollar( round(1000*mean.x,0)) ), 
      col="darkorange", cex=1.8, pos=3 )

median.x <- median( mhv.change/1000, na.rm=T )
abline( v=median.x, col="dodgerblue", lwd=2, lty=2 )
text( x=200, y=2000, 
      labels=paste0( "Median = ", dollar( round(1000*median.x,0)) ), 
      col="dodgerblue", cex=1.8, pos=3 )
```

**Percent change in MHV 2000 to 2010**
```{r}
hg <-
hist( mhv.growth, breaks=5000, 
      xlim=c(-100,200), yaxt="n", xaxt="n",
      xlab="", cex.main=1.5,
      ylab="", main="Growth in Home Value by Census Tract 2000 to 2010",
      col="gray40" )

axis( side=1, at=seq( from=-100, to=200, by=50 ), 
      labels=paste0( seq( from=-100, to=200, by=50 ), "%" ) )

ymax <- max( hg$count )
        
mean.x <- mean( mhv.growth, na.rm=T )
abline( v=mean.x, col="firebrick", lwd=2, lty=2 )
text( x=75, y=(0.5*ymax), 
      labels=paste0( "Mean = ", round(mean.x,0), "%"), 
      col="firebrick", cex=1.2, pos=4 )

median.x <- median( mhv.growth, na.rm=T )
abline( v=median.x, col="darkgreen", lwd=2, lty=2 )
text( x=75, y=(0.6*ymax), 
      labels=paste0( "Median = ", round(median.x,0), "%"), 
      col="darkgreen", cex=1.2, pos=4 )
```
**Part 01 : Select three Independent Variables**

For this exercise, I selected :

**-Household Income in the tract. Areas with higher household incomes will be more attractive to buyers and will drive home prices up** 
**-Percent College-Educated Residents. More educated residents provides ease for employment and job security resulting in availability of income for home purchase. As a result drive home prices up.**
**-An increase in owner-occupied units is proof of proper maintenance of residences thus maintaining prices at a stable rate**

**Part 02 : Variable Skew**

```{r}
par( mfrow=c( 2,2 ) )

hist( d$p.own, xlim = c(0,80), breaks=50, col="blue", border="white",
      yaxt="n", xlab="", ylab="", main="Percent Owner-Occupied Units")
hist( d$p.col, xlim = c(0,80), breaks=50, col="red", border="white",
      yaxt="n", xlab="", ylab="", main="Percentage of College-Educated Residents")
hist( d$hinc00, xlim = c(0,200000), breaks=50, col="gray20", border="white",
      yaxt="n", xlab="", ylab="", main="Household Income Distribution")
```

**Based on the histogram, we note left and right variable skew for owner-occupied units and college-educated residents respectively.Household Income appears to be uniformly distributed. However, we carry out a log transformation for all the variables.** 

```{r}
# transform the variables
d$log.p.own  <- log( d$p.own + 1  )
d$log.p.col <- log( d$p.col + 1 )
d$log.hinc00 <- log( d$hinc00 + 1 )

# examine the distribution
par( mfrow=c( 3,2 ) )

hist( d$p.own, xlim = c(0,80), breaks=50, col="blue", border="white",
      yaxt="n", xlab="", ylab="", main="Percent Owner-Occupied Units")
hist( d$log.p.own, breaks=50, col="blue", border="white",
      yaxt="n", xlab="", ylab="", main="Percent Owner-Occupied Units (logged)")
hist( d$p.col, xlim = c(0,80), breaks=50, col="red", border="white",
      yaxt="n", xlab="", ylab="", main="Percentage of College-Educated Residents")
hist( d$log.p.col, breaks=50, col="red", border="white",
      yaxt="n", xlab="", ylab="", main="Percentage of College-Educated Residents (logged)")
hist( d$hinc00, xlim = c(0,200000), breaks=50, col="gray20", border="white",
      yaxt="n", xlab="", ylab="", main="Household Income Distribution")
hist( d$log.hinc00, breaks=50, col="gray20", border="white",
      yaxt="n", xlab="", ylab="", main="Household Income Distribution (logged)")
```

**Part 03 : Multicollinearity**

```{r}
# grab the variables we want
plotd <- d %>% 
  select( mhv.growth, log.p.own, log.p.col, log.hinc00 )

set.seed( 1234 )
plotd <- sample_n( plotd, 5000 ) %>% 
  na.omit()

# plot the data and show the correlations
pairs( plotd, upper.panel=panel.cor, lower.panel=panel.smooth )
```

**Part 4 : Relationship of Home values with Predictors**

```{r}
par( mfrow = c( 2,2 ) )

jplot( plotd$log.p.own, plotd$mhv.growth, ylim=c( -50,100 ),
       lab1="Percent Owner-Occupied Units (logged)", lab2="MHV Growth" )

jplot( plotd$log.p.col, plotd$mhv.growth, ylim=c( -50,100 ),
       lab1="Percentage of College-Educated Residents (logged)", lab2="MHV Growth" )

jplot( plotd$log.hinc00, plotd$mhv.growth, ylim=c( -50,100 ),
       lab1="Household Income Distribution (logged)", lab2="MHV Growth" )
```
**Part 4: Descriptives**

```{r}
df <- data.frame( MedianHomeValue2000=d$mhv.00, 
                  MedianHomeValue2010=d$mhv.10, 
                  MHV.Change.00.to.10=d$mhv.change,
                  MHV.Growth.00.to.12=d$mhv.growth,
                  OwnLog2000=d$log.p.own,
                  ColLog2000=d$log.p.col,
                  HincLog2000=d$log.hinc00 )

stargazer( df, 
           type=s.type, 
           digits=0, 
           summary.stat = c("min", "p25","median","mean","p75","max") )
```

**The typical change in home value between 2000 and 2010 is 60,047. The largest change in home value between 2000 and 2010 is 1,000,001.**

```{r}
jplot( df$MHV.Change.00.to.10, df$MHV.Growth.00.to.12, ylim=c( -50,100 ),
       lab1="MHV Change", lab2="MHV Growth" )
```

**Part 05 : Models**

```{r}
m1<-lm( MHV.Change.00.to.10 ~ OwnLog2000 + ColLog2000 + HincLog2000, data=df )

m2<-lm( MHV.Growth.00.to.12 ~ OwnLog2000 + ColLog2000 + HincLog2000, data=df )


stargazer( m1, m2, 
           type=s.type, digits=2,
           omit.stat = c( "rsq","f" ) )
```
**All the 03 (three) variables are significant predictors in our models. The regression table indicate that for both change in median house value and growth in median house value:**

**-lower owner-occupancy in 2000 led to decreased change/growth in median house value between 2000 and 2010;**

**-higher household incomes in 2000 led to increased change/growth in median house value between 2000 and 2010;**

**-higher college-educated residents in 2000 led to an increase change in median house value between 2000 and 2010, and simultaneously a decrease growth in median home values between 2000 and 2010.**

**Of these three variables, owner-occupied units had the largest effect for change in median house value and household incomes had the largest effect for median home value and growth in median home values.**


**Part 6 : Effect Size**

```{r}
predictors <- cbind( 
  df$OwnLog2000, df$ColLog2000, df$HincLog2000 )

x.75 <- NULL
x.25 <- NULL

for ( i in 1:3 ){
x.75[i] <- quantile( predictors[,i], p=0.75, na.rm = TRUE )  
x.25[i] <- quantile( predictors[,i], p=0.25, na.rm = TRUE )  
}

beta.x.m1 <- m1$coefficients[2:4]
beta.x.m2 <- m2$coefficients[2:4]

effect.size.x.m1 <- ( x.75 - x.25 ) * beta.x.m1 
effect.size.x.m2 <- ( x.75 - x.25 ) * beta.x.m2 
```



```{r}
# WRITE TO FILE 

library( geojsonio )

sd_dorling <- spTransform( sd_dorling, CRS("+proj=longlat +datum=WGS84") )
geojson_write( sd_dorling, file="sd_dorling.geojson", geometry="polygon" )

```


```{r}
# Convert to sf object if needed
sd_dorling_sf <- st_as_sf(sd_dorling)

# Save as GeoJSON
library(geojsonio)
geojson_write(sd_dorling_sf, file = "sd_dorling.geojson")

```


```{r}
library( geojsonio )
library( sp )

# load from github
github.url <- "https://raw.githubusercontent.com/ElvisYoh/sd_dorling.geojson/main/sd_dorling.geojson"
sd <- geojson_read( x=github.url,  what="sp" )

plot( sd )
```


```{r}
###################################
#
#     STARGAZER SETTINGS
#
###################################

# DO NOT RUN CHUNK UNLESS KNITTING:
# changes table formats to html
# before rendering RMD docs

s.type <- "html"
```


